---
title: "MATH4753ROSAlab8"
author: "Brandan Rosa"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753ROSAlab8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(MATH4753ROSAlab8)
```

# Introduction

This package is primarily concerned with simulations of continuous distributions; the Uniform and the Gamma distributions particularly. The package contains three functions and a shiny app. Two of the functions, "mysimA" and "mysimB" simulate a `unif(0,1)` and a `gamma(2,1)`, respectively. 

The function "rmyF" simulates an objective function `B` where B is distributed `gamma(2,1)`. Further, this function seeks to find the roots of the underlying function- that is to calculate the minimum of the absolute value of the objective function.

Finally the shiny app, "lab8shiny" allows the user to type in a number of iterations to simulate the `B` function from "rmyF". The functions also produce a named list with various summary statistics.

# Examples 

## `mysimA(iter = 10000)`

```{r, fig.align = "center", fig.width=7, fig.height=5}
mysimA(iter = 10000)
```

## `mysimB(iter = 10000)`

```{r, fig.align = "center", fig.width=7, fig.height=5}
mysimB(iter = 10000)
```

## `rmyF(iter = 10000)`

```{r, fig.align = "center", fig.width=7, fig.height=5}
rmyF(iter = 10000)
```

## lab8shiny

To view this app, run the following code in `R`

`shiny::runGitHub(repo = "MATH4753ROSAlab8", username = "brandanrosa", subdir = "inst/Lab8shiny")`















